Icicle: write once, run once

### 2016-05-30 2016fhpc/section/03-Core.tex
some minor changes and remove GVN stuff from related
Adjust spacing in intermediate language section

\begin{code}
Exp   := x | Prim Exp*

Plan  := plan   x { (x : T;)* }
       before { x : T = Exp;* }
       folds  { x : T = Exp then Exp;* }
       after  { x : T = Exp;* }
       return { x : T = x;* }
\end{code}

@@

==>

plan stocks { open : Int; close : Int; }
before { }
folds  { count : Int = 0 then count + 1 }
after  { }
return { count_query : Int = count }
\end{code}

@@

==>

plan stocks { open : Int; close : Int; }
before { }
folds  { sum : Int = 0 then sum + open }
after  { }
return { sum_open : Int = sum }
\end{code}

@@

==>

plan stocks { open : Int; close : Int; }
before { }
folds  { sum       : Int = 0 then sum + open 
         count     : Int = 0 then count + 1 }
after  { mean      : Int = sum / count }
return { mean_open : Int = mean }
\end{code}

@@

An efficient imperative loop can be generated from this query plan rather easily, in a similar way as previous work on flow fusion\cite{lippmeier2013data}.

>>>>

\begin{tabbing}
MMM \= MM \= MMMM \= MM \= MMMMMM \= \kill
$\mi{PlanX}$
\GrammarDef
  $x~|~@Int@~|~\mi{Prim}~\ov{\mi{PlanX}}$
\\
\\
$\mi{Plan}$
\GrammarDef
  $@plan@~x$ \> $\{~\ov{x~:~T;}~\}$
\\
  \> \> $@before@$ \> $\{~\ov{x~:~T~=~\mi{PlanX};}~\}$ \\
  \> \> $@folds@$  \> $\{~\ov{x~:~T~=~\mi{PlanX}~@then@~\mi{PlanX};}~\}$ \\
  \> \> $@after@$  \> $\{~\ov{x~:~T~=~\mi{PlanX};}~\}$ \\
  \> \> $@return@$ \> $\{~\ov{x~:~T~=~x;}~\}$ \\
\end{tabbing}

@@

==> plan stocks { open : Int; close : Int; }
    before { }
    folds  { count : Int = 0 then count + 1 }
    after  { }
    return { count_query : Int = count }
\end{code}

@@

==> plan stocks { open : Int; close : Int; }
    before { }
    folds  { sum : Int = 0 then sum + open }
    after  { }
    return { sum_open : Int = sum }
\end{code}

@@

==> plan stocks { open : Int; close : Int; }
    before { }
    folds  { sum       : Int = 0 then sum + open 
             count     : Int = 0 then count + 1 }
    after  { mean      : Int = sum / count }
    return { mean_open : Int = mean }
\end{code}

@@

An efficient imperative loop can be generated from this query plan rather easily, in a similar way as previous work on flow fusion~\cite{lippmeier2013data}.
